Web Processing - Standardised GIS Analyses for Cable Route Planning

### 2023-01-11 paper/paper-CableRoute.tex
updated paper:
added maps that shows least cost paths for combinations different resolutions and values for parameter all touched.

\documentclass[acmtog]{acmart}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage[acronym]{glossaries}
\usepackage{todonotes}
\usepackage{tikz}

@@

	Hence, the mean minimum euclidean distance between the two paths can used to compute
	the similarity.
	As different table~\ref{table:2} shows the distance between the two paths decreases
	with increasing resolution.
	At the same time the differences in the aggregated costs stay constant.
	\todo{Interpretation} When normalize the aggregated costs by the resolution.
	Than On one hand it can be seen, that the all\_touched False under estimate the costs and that this tendency scales
	linear with the resolution.
	On the other hand, the all\_touched True least cost over estimates the aggregated costs on a linear scale of
	the resolution.
	Therefore, the difference for the normalized least cost paths is reduced on scale by the resolution.\todo{show map}

@@

	Comparing the all\_touched True rasterization and all\_touched False for the same resolution in contrast with the paths of all\_touched False rasterization at the
	different resolutions the later paths are more similar.
	The mean average distance between the 100 m resolution run and the 5 m resolution run is 257.97 m.

@@

	Hence, in an overall perspective paths of the all\_touched False runs stay in a
	similar region, while paths of the all\_touched True coverage strongly to the paths all\_touched False runs.
	On a more detailed level, it can be seen, that also the Paths of all\_touched 	converges the all\_touched True path.
	But the extent is smaller.
	The length of the the paths only differs to a maximum of about 10 \%.
	The least path distance for higher resolutions can be lower, because new paths, between regions that are forbidden
	in higher resolution can open.
	On the other side the length of the paths can increase, because with higher resolution more vertices will be used.

	The zonal stat (see table\ref{table:3}) for a buffer of 100 m (5 m) around the path has been used, to estimate the
	percentage of which costs levels are around the path.
	When using all\_touched True rasterization with higher resolution the tendency is to use a higher percentage of the
	Preferential Level and less the NoRestriction Level.\todo{Interpretation:}
	The ratio of the 100 m buffered least cost path, strongly shifted  to Levels lower costs.
	\todo{Interpretation: Interpretation the Cost Paths are much nearer smaller, than 100 m! No problem because buffering is included in the cost raster.}
	There is no strong tendency for the all\_touched False least cost paths.

@@

	\begin{table*}[t]
		\caption{\acrfull{r} Category percentages of each least cost path for a buff of 100 m (5 m) around the least cost path.}
		\label{table:3}
		\centering
		\begin{tabular}{ r  r  r r  r r  r r  r r  r r}
			resolution /m & all touched & \multicolumn{2}{c}{ $ r_{Preferential} \% $}  & \multicolumn{2}{c}{ $ r_{No Restriction} \% $ }  & \multicolumn{2}{c}{ $ r_{Restricted} \% $}  & \multicolumn{2}{ c }{ $ r_{strongly Restricted}\% $ } & \multicolumn{2}{c}{ $ r_{Prohibited} \% $ } \\
			\hline
			5 & False &  4.7  &  (5.4) & 58.7 & (58.9) & 8.8 & (8.4) & 0.7 & (0.7) & 27.1 & (26.7)  \\

>>>>

\documentclass[acmtog]{acmart}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{subfig}
\usepackage[acronym]{glossaries}
\usepackage{todonotes}
\usepackage{tikz}

@@

	Hence, the mean minimum euclidean distance between the two paths can used to compute
	the similarity.
	As different table~\ref{table:2} shows the distance between the two paths decreases
	with increasing resolution. In addition, this tendency is depicted in figure~\ref{fig:paths_alltouched} for the calculated cost paths of 5m and 100 m resolutions.

	At the same time the differences in the aggregated costs stay constant.
	\todo{Interpretation} When normalize the aggregated costs by the resolution.
	Than On one hand it can be seen, that the all\_touched False under estimate the costs and that this tendency scales
	linear with the resolution.
	On the other hand, the all\_touched True least cost over estimates the aggregated costs on a linear scale of
	the resolution.
	Therefore, the difference for the normalized least cost paths is reduced on scale by the resolution.\todo{show map}

	\begin{figure}
		\centering

		\subfloat[\centering resolution of 5 m.]{{\includegraphics[width=.45\linewidth]{./images/LeastCostPaths_5m.pdf} }}%
		\qquad
		\subfloat[\centering resolution of 100 m.]{{\includegraphics[width=.45\linewidth]{./images/LeastCostPaths_100m.pdf} }}%
		\caption{Figures of the least cost paths. Contrasting the paths for different resolutions. Using OpenStreetMaps as base map.}
		\label{fig:paths_resolution}
	\end{figure}

	\begin{figure}
	\centering

	\subfloat[\centering all touched false.]{{\includegraphics[width=.45\linewidth]{./images/LeastCostPaths_al_F.pdf} }}%
	\qquad
	\subfloat[\centering all touched true.]{{\includegraphics[width=.45\linewidth]{./images/LeastCostPaths_al_T.pdf} }}%

	\caption{Figures of the least cost paths. Contrasting the changes of the least cost paths for the different results, depending on the parameter all\_touched. Using OpenStreetMaps as base map.}
	\label{fig:paths_alltouched}
\end{figure}

@@

	Comparing the all\_touched True rasterization and all\_touched False for the same resolution in contrast with the paths of all\_touched False rasterization at the
	different resolutions the later paths are more similar.
	The mean average distance between the 100 m resolution run and the 5 m resolution run is 257.97 m. \todo{Option add 2.5 m and 25 m}

@@

	Hence, in an overall perspective paths of the all\_touched False runs stay in a
	similar region, while paths of the all\_touched True coverage strongly to the paths all\_touched False runs. This behaviour is depicted in figure~\ref{fig:paths_alltouched}. 
	On a more detailed level, it can be seen, that also the Paths of all\_touched 	converges the all\_touched True path.
	But the extent is smaller.
	The length of the the paths only differs to a maximum of about 10 \%.
	The least path distance for higher resolutions can be lower, because new paths, between regions that are forbidden
	in higher resolution can open.
	On the other side the length of the paths can increase, because with higher resolution more vertices will be used.

	The zonal stat (see table~\ref{table:3}) for a buffer of 100 m (5 m) around the path has been used, to estimate the
	percentage of which costs levels are around the path.
	When using all\_touched True rasterization with higher resolution the tendency is to use a higher percentage of the
	Preferential Level and less the NoRestriction Level.\todo{Interpretation:}
	The ratio of the 100 m buffered least cost path, strongly shifted  to Levels lower costs.
	\todo{Interpretation: Interpretation the Cost Paths are much nearer smaller, than 100 m! No problem because buffering is included in the cost raster.}
	There is no strong tendency for the all\_touched False least cost paths.

@@

	\begin{table*}[t]
		\caption{\acrfull{r} of Category percentages of each least cost path for a buff of 100 m (5 m) around the least cost path.}
		\label{table:3}
		\centering
		\begin{tabular}{ r  r  r r  r r  r r  r r  r r}
			resolution /m & all touched & \multicolumn{2}{c}{ $ r_{Preferential} \% $}  & \multicolumn{2}{c}{ $ r_{No Restriction} \% $ }  & \multicolumn{2}{c}{ $ r_{Restricted} \% $}  & \multicolumn{2}{ c }{ $ r_{strongly Restricted}\% $ } & \multicolumn{2}{c}{ $ r_{Prohibited} \% $ } \\
			\hline
			5 & False &  4.7  &  (5.4) & 58.7 & (58.9) & 8.8 & (8.4) & 0.7 & (0.7) & 27.1 & (26.7)  \\
